### 2023-04-20 paper.Rmd
explain notation for mean values in t moment variables

$$
\mathit{SSE_{kplusGeneralized}} =
  \sum\limits_{t=1}^{T} 
  w_t \left(
  \sum\limits_{j=1}^{P} 
  \sum\limits_{k=1}^{K} 
  \sum\limits_{i \in C_k}
  (x_{tij} - \overline{x}_{tj} ^{(k)})^2
  \right)
$$

Here, $w_t$ is the weight associated with the $t$'th moment and $\overline{x}_{tj} ^{(k)}$ is the $k$'th group mean on the $j$'th $t$-moment variable. Maximizing $\mathit{SSE_{kplusGeneralized}}$ can be used to minimize differences with regard to the first $T$ distribution moments between $K$ groups.

>>>>

$$
\mathit{SSE_{kplusGeneralized}} =
  \sum\limits_{t=1}^{T} 
  w_t \left(
  \sum\limits_{j=1}^{P} 
  \sum\limits_{k=1}^{K} 
  \sum\limits_{i \in C_k}
  (\hat{x}_{tij} - \overline{x}_{tj} ^{(k)})^2
  \right)
$$

Here, $w_t$ is the weight associated with the $t$'th moment and $\overline{\mathbf{X}}^{(k)}_{T \times P} = \{\overline{x}_{tj}^{(k)}\}_{T \times P}$ is a centroid matrix containing the mean values for all $t$-moment variables in the $k$'th group, i.e.

$$
\overline{x}_{tj}^{(k)} = \frac{1}{n_k} \sum_{i \in C_k} \hat{x}_{tij}
$$

Maximizing $\mathit{SSE_{kplusGeneralized}}$ can be used to minimize differences with regard to the first $T$ distribution moments between $K$ groups.
